Are populations like a circuit? Comparing isolation by resistance to a new coalescent-based method.

### 2019-04-21 isolation_by_coalescence.tex
resubmission version

\begin{figure}
\centering
    \includegraphics[width=0.65\textwidth]{poplars/posterior_dists_g_populus}
    \includegraphics[width=0.65\textwidth]{poplars/grid_populus}
    \caption{
        Posterior distributions of parameters for \textit{Populus} data,
        using coalescence time inference with the model shown in Figure~\ref{fig:poplar_results}.
        \textbf{(top)} Posterior medians (dark line),
        interquartile range (box), and min--max (whiskers),
        for gene flow rates.
        \textbf{(bottom)} Posterior medians gene flow rates, 
        both as a numerical label and color
        (as in other figures, red is lower and blue is larger),
        along with edge labels that match the upper figure.
        Nodes are also colored according to posterior median coalescence rate:
        grey is a high rate (small population)
        and orange is a low rate (large population).
        \label{sfig:poplar_g}
    }
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=\textwidth]{poplars/posterior_dists_gam_populus}
    \caption{
        Posterior distributions of parameters for \textit{Populus} data,
        using coalescence time inference with the model shown in Figure~\ref{fig:poplar_results}.
        Plot shows posterior medians (dark line),
        interquartile range (box), and min--max (whiskers),
        for coalescence rates, labeled as in Figure~\ref{fig:poplar_results}.
        For instance, the coalescence rates for regions 4 and 8 (labeled ``gam4'' and ``gam8'')
        are inferred to be much smaller than most other regions, 
        perhaps indicating larger or older populations in southwestern British Columbia.
        \label{sfig:poplar_gam}
    }
\end{figure}

>>>>

\begin{figure}
\centering
    \includegraphics[width=0.65\textwidth]{poplars/posterior_dists_g_populus}
    \includegraphics[width=0.65\textwidth]{poplars/grid_populus}
    \caption{
        Posterior distributions of parameters for \textit{Populus} data,
        using coalescence time inference with the model shown in Figure~\ref{fig:poplar_results}.
        \textbf{(top)} Posterior medians (dark line),
        approximate middle 50\% (box), and 90\% (whiskers),
        for gene flow rates.
        \textbf{(bottom)} Posterior medians gene flow rates, 
        both as a numerical label and color
        (as in other figures, red is lower and blue is larger),
        along with edge labels that match the upper figure.
        Nodes are also colored according to posterior median coalescence rate:
        grey is a high rate (small population)
        and orange is a low rate (large population).
        \label{sfig:poplar_g}
    }
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=\textwidth]{poplars/posterior_dists_gam_populus}
    \caption{
        Posterior distributions of parameters for \textit{Populus} data,
        using coalescence time inference with the model shown in Figure~\ref{fig:poplar_results}.
        Plot shows posterior medians (dark line),
        approximate middle 50\% (box), and 90\% (whiskers),
        for coalescence rates, labeled as in Figure~\ref{fig:poplar_results}.
        For instance, the coalescence rates for regions 4 and 8 (labeled ``gam4'' and ``gam8'')
        are inferred to be much smaller than most other regions, 
        perhaps indicating larger or older populations in southwestern British Columbia.
        \label{sfig:poplar_gam}
    }
\end{figure}
